On change of priors in one-vs-one classification methods

### 2025-05-07 paper.tex
Introduce odds notation

\begin{prop}[Fundamental theorem of one-vs-one classification]
	 \label{prop:binary2multi}
	 Knowledge of binary Bayes classifiers $p_{ij}^\Pi$ determines the multiclass Bayes classifier $\boldsymbol{p}^\Pi$.
\end{prop}
\begin{proof}
	Indeed, from \eqref{eq:bt1} we deduce the odds of classes $C_j$ to $C_i$
	\begin{align}
	\frac{p_j^\Pi(x)}{p_j^\Pi(x)} = \frac{1}{p^\Pi_{ij}(x)}- 1.
	\end{align}
	Knowing the odds of $C_2$ to $C_1$, $C_3$ to $C_2$ up to $C_{K}$ to $C_{K-1}$ together with the requirement that probabilities sum to one uniquely determines the whole vector $\boldsymbol{p}^\Pi(x)$.
\end{proof}
%\begin{proof}
%Indeed, we have 
%\begin{align*}
%\frac{1}{r_{ij}(x)} - 1 = \frac{p_j^\Pi}{p_i^\Pi}
%\end{align*}
%\end{proof}

@@

Suppose real numbers $\alpha_1, \ldots,\alpha_M$ are real numbers and $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are probabibilistic multi-class classification methods satisfying Assumption \ref{ass:1}. We define their linear combination $\bigoplus_i a_m \boldsymbol{v}_m$ as the classification method that for any $x$ yields the probability distribution on $K$ classes that satisfies
\begin{align*}
 	\bigl(a_1 \boldsymbol{v}_1 \oplus \ldots \oplus a_M \boldsymbol{v}_M\bigr)(x) \propto \boldsymbol{v}_1^{a_1}(x) \odot \cdots \odot \boldsymbol{v}_M^{a_M}(x),
\end{align*}
where the symbol $\odot$ denotes componentwise multiplication, and exponentials are computed component-wise. With this definition we can state the following result.

>>>>

\begin{prop}[Fundamental theorem of one-vs-one classification]
	 \label{prop:binary2multi}
	 Knowledge of binary Bayes classifiers $p_{ij}^\Pi$ determines the multiclass Bayes classifier $\boldsymbol{p}^\Pi$.
\end{prop}
\begin{proof}
	Given a multiclass distribution $\boldsymbol{p} = (p_1, \ldots,p_K)$ on $K$ classes, let $\alpha_{ij}(\boldsymbol{p})$ denotes the odds of $C_i$ to $C_j$:
	\begin{align}
		\alpha_{ij}(\boldsymbol{p}) = \frac{p_i}{p_j}
	\end{align}

	From \eqref{eq:bt1} we can deduce the odds of classes $C_j$ to $C_i$ as
	\begin{align}
	\alpha_{ij}(\boldsymbol{p}^\Pi) = \frac{p_j^\Pi(x)}{p_j^\Pi(x)} = \frac{1}{p^\Pi_{ij}(x)}- 1.
	\end{align}
	Knowing the odds of $C_2$ to $C_1$, $C_3$ to $C_2$ up to $C_{K}$ to $C_{K-1}$ together with the requirement that probabilities sum to one uniquely determines the whole vector $\boldsymbol{p}^\Pi(x)$.
\end{proof}
%\begin{proof}
%Indeed, we have 
%\begin{align*}
%\frac{1}{r_{ij}(x)} - 1 = \frac{p_j^\Pi}{p_i^\Pi}
%\end{align*}
%\end{proof}

@@

Suppose real numbers $a_1, \ldots,a_M$ are real numbers and $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are probabibilistic multi-class classification methods satisfying Assumption \ref{ass:1}. We define their linear combination $\bigoplus_i a_m \boldsymbol{v}_m$ as the classification method that for any $x$ yields the probability distribution on $K$ classes that satisfies
\begin{align*}
 	\bigl(a_1 \boldsymbol{v}_1 \oplus \ldots \oplus a_M \boldsymbol{v}_M\bigr)(x) \propto \boldsymbol{v}_1^{a_1}(x) \odot \cdots \odot \boldsymbol{v}_M^{a_M}(x),
\end{align*}
where the symbol $\odot$ denotes componentwise multiplication, and exponentials are computed component-wise. With this definition we can state the following result.
